---
# title: "Vector declaration"
author: "Issac Lee"
date: "`r Sys.Date()`"
output: markdowntemplates::skeleton
---
## How to declare vector in R

One easy way to declare vector in R is to use 'c()' commend. Here is a sample code for declaration of a vector
$$
a=\left(\begin{array}{c}
1\\
2\\
3
\end{array}\right)
$$
```{r echo = TRUE}
a <- c(1,2,3)
a
```

There are many opinion about the meaning of 'c' here. Some people argue that 'c' stands for 'combine' while the other people insist that it stands for 'concatenate'.(http://stackoverflow.com/questions/11488820/why-use-c-to-define-vector)

Each argue has its own rational but for me, I would say it is more convinent for me to memorize that it stands for 'colum' since it gives us a colum vector.
To check the result of the code is a colum vector, we can confirm its transpose as follows:
```{r}
t(a)
```
As we see that the transpose of a is a row vector, thus a itself is a colum vector. It is good to know this fact since it sometimes gives you a totally different calculation result.
For example, depending on the order of matrix calculation, it could be a matrix or a number.
$$
a^{t}a=\left(\begin{array}{ccc}
1 & 2 & 3\end{array}\right)\left(\begin{array}{c}
1\\
2\\
3
\end{array}\right)
$$
The above dot product of vector a can be written as R code as follows:
```{r}
t(a) %*% a
```

However, if we switch the order, the result will be a 3-by-3 matrix as follows:
$$
aa^{t}=\left(\begin{array}{c}
1\\
2\\
3
\end{array}\right)\left(\begin{array}{ccc}
1 & 2 & 3\end{array}\right)
$$
```{r}
a %*% t(a)
```

Note that %*% command is used to calculate the matrix operation here.


```{r bib, include=FALSE}
# KEEP THIS AT THE END OF THE DOCUMENT TO GENERATE A LOCAL bib FILE FOR PKGS USED
knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='skeleton.bib')
```