---
# title: "Vector filtration"
author: "Issac Lee"
date: "`r Sys.Date()`"
output: markdowntemplates::skeleton
---
## Vector filtration in R

So far, we have learn how to define vector in R. In this post, we will take a look at the way to manipulate the defined vectors. By using bracket, **[ ]**, command, user can sellect the specific element in the defined vector.

Let us assume that we have already a vector named "x":
```{r}
x <- c(1:10)
x
```
Then, if we want to pick the second element of vector "x", the following command can be used as follows:
```{r}
x[2]
```
Thus, there is another way to define a new vector by using **[ ]** command. The following code can generate a vector named "y" whose elements are consist of the first and third element of vector "x".
```{r}
y <- x[c(1,3)]
y
```
Wonderfull thing in R is that We can use all the methods that we studied in the previous post to pick specific elements. In other word, there are many ways to manipulate the defined vector. Here are some examples:

First, if we want to take the first half of the elements in "x", then we can pick as follows:
```{r}
y <- x[1:5]
y
```
Second, if we want to take the 3rd the element in "x" and repeat 4 times, then we can do as follows:
```{r}
y <- x[rep(3,4)]
y
```
Third, in the case of picking the even positioned in vector "x", we can cleverly use the arithmatic rules of R as follows:
```{r}
y <- x[1:5*2]
y
```
To understand the above command, let us take a look at the in side of the bracket first.
```{r}
1:5 * 2
```
In R, if we multiply the number to the vector, R automatically understand as the scalar mutiplication to the vector in math as follows:
$$
2a=2\times\left(\begin{array}{c}
1\\
2\\
3\\
4\\
5
\end{array}\right)=\left(\begin{array}{c}
2\\
4\\
6\\
8\\
10
\end{array}\right)
$$
Thus, the above command, **x[1:5*2]**, is actually same as defining vector "y" as follows:
```{r}
y <- x[c(2,4,6,8,10)]
y
```
What do we do for generating the vector whose elements are odd positioned in vector "x"? Hint: you can just substract 1.


```{r bib, include=FALSE}
# KEEP THIS AT THE END OF THE DOCUMENT TO GENERATE A LOCAL bib FILE FOR PKGS USED
knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='skeleton.bib')
```